Paper 1: Triangulating trends in inequality around the world from secondary databases

### 2022-10-11 PhD_pages/paper_pages/paper1.qmd
testing out PhD workflow

Is it that there has been a secular rise - suggesting global forces.

Or is it mixed - suggesting much scope for national policy to influence?

@@

Untangle which methods, definitions.

@@

## Coverage

## Lining up methods

@@

## Comparing distributions

>>>>

@@

Which world we live in matters for how we think we should tackle inequality.

A secular, general rise - suggesting global forces, perhaps something intrinsic to capitalism (Piketty, 2014).

A mixed picture of inequality around the world suggests reflect specific circumstances, with accordingly much scope for national policy to influence.

Both are reasonable methods and have strengths and weaknesses.

I want to:

a\) Triangulate the key stylized facts. Which observations are robust to across available datasets with their different methods, and which are contingent?

b\) Untangle which methods, definitions affect the different conclusions arrived at.

@@

### Coverage

s

## Methods: Comparing databases

### Lining up years

@@
